\LARGE \bf Constrained Optimization-Based Neuro-Adaptive Control (CONAC) for Constrained Systems

### 2025-05-19 IWIS_manuscript.tex
IWIS update final

\documentclass[letterpaper, 10 pt, conference]{ieeeconf}  % Comment this line out if you need a4paper

@@

\overrideIEEEmargins                                      % Needed to meet printer requirements.

\makeatletter
\let\NAT@parse\undefined
\makeatother

@@

\title{\LARGE \bf
    WIP: Constrained Optimization-Based Neuro-Adaptive Control (CONAC) for Constrained Systems
}

\author{Myeongseok Ryu, and Kyunghwan Choi% <-this % stops a space
    \thanks{
        Myeongseok Ryu and Kyunghwan Choi are with the Cho Chun Shik Graduate School of Mobility, Korea Advanced Institute of Science and Technology (KAIST), Daejeon 34051, Republic of Korea {\tt\small \{dding\_98, kh.choi\}@kaist.ac.kr}
    }%
}

@@

\maketitle
\thispagestyle{empty}
\pagestyle{empty}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
    This paper reports on work in progress to review and improve the effectiveness of the constrained optimization-based neuro-adaptive control (CONAC) for weight, control input, and state constraints.
    Our preliminary results show that the CONAC can handle the weight constraints and control input constraints.
  A deep neural network (DNN) is employed to approximate the ideal stabilizing control law while simultaneously learning the unknown system dynamics and addressing the constraints within a constrained optimization framework.
  The weight adaptation laws are formulated to solve the defined constrained optimization problem, ensuring satisfaction of first-order optimality conditions at steady state.
  The controller's stability is rigorously analyzed using Lyapunov theory, guaranteeing bounded tracking errors and bounded DNN weights. 
  The CONAC is validated through a real-time implementation on a 2-DOF robotic manipulator, demonstrating its effectiveness in achieving accurate trajectory tracking while satisfying all imposed constraints.
  Finally, we discuss the extension of the CONAC to handle state constraints, which is a crucial aspect for practical applications in various engineering systems.
\end{abstract}

@@

The stability of the CONAC under weight constraints was rigorously analyzed using Lyapunov theory, \ie see, Theorem 1 in \cite{Ryu:2024aa}.
The theorem guarantees that the tracking error $\mv{e}$ and the DNN weights $\estwth$ are bounded, ensuring that weight constraints are satisfied.

@@

The adaptation law is derived using the same approach as in \eqref{eq:adaptation law}.
The stability of the extended CONAC was also analyzed using Lyapunov theory, ensuring that the tracking error $\mv{e}$ and the DNN weights $\estwth$ are bounded, and the control input constraints are satisfied.

>>>>

% \documentclass[letterpaper, 10 pt, conference]{ieeeconf}  % Comment this line out if you need a4paper
\documentclass[conference]{IEEEtran}

@@

% \overrideIEEEmargins                                      % Needed to meet printer requirements.

% \makeatletter
% \let\NAT@parse\undefined
% \makeatother

@@

% correct bad hyphenation here
\hyphenation{op-tical net-works semi-conduc-tor}
\pagestyle{empty}

@@

\title{\LARGE \bf
    Constrained Optimization-Based Neuro-Adaptive Control (CONAC) for Constrained Systems
}

\author{
    \IEEEauthorblockN{1\textsuperscript{st}\,Myeongseok\,Ryu and 2\textsuperscript{nd}\,Kyunghwan\,Choi}
    \IEEEauthorblockA{\textit{Cho Chun Shik Graduate School of Mobility} \\
    \textit{Korea Advanced Institute of Science and Technology}\\
    Daejeon, Republic of Korea \\
    \{dding\_98, kh.choi\}@kaist.ac.kr}
    }

\maketitle
\thispagestyle{empty}
% \pagestyle{empty}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
    This paper reports on work in progress to review and improve the effectiveness of the constrained optimization-based neuro-adaptive control (CONAC) for weight, control input, and state constraints.
    Our preliminary results show that the CONAC can handle the weight constraints and control input constraints.
  A neural network (NN) was employed to approximate the ideal stabilizing control law while simultaneously learning the unknown system dynamics and addressing the constraints within a constrained optimization framework.
  The controller's stability was rigorously analyzed using Lyapunov theory, guaranteeing bounded tracking errors and bounded NN weights. 
  The CONAC was validated through a real-time implementation on a 2-DOF robotic manipulator, demonstrating its effectiveness in achieving accurate trajectory tracking while satisfying all imposed constraints.
  Finally, we discuss the extension of the CONAC to handle state constraints, which is a crucial aspect for practical applications in various engineering systems.
\end{abstract}
\begin{IEEEkeywords}
	Neuro-adaptive control, Constrained Optimization, Constrained Systems
\end{IEEEkeywords}

@@

The stability of the CONAC under weight constraints was rigorously analyzed using Lyapunov theory, \ie see, Theorem 1 in \cite{Ryu:2024aa}.
The theorem guarantees that the tracking error $\mv{e}$ and the NN weights $\estwth$ are bounded, ensuring that weight constraints are satisfied.

@@

The adaptation law is derived using the same approach as in \eqref{eq:adaptation law}.
The stability of the extended CONAC was also analyzed using Lyapunov theory, ensuring that the tracking error $\mv{e}$ and the NN weights $\estwth$ are bounded, and the control input constraints are satisfied.
